---
title: "Untitled"
author: "Mohd Azmi"
date: "11/16/2020"
output:
  slidy_presentation: default
  beamer_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Example - Mediation and confounder

Among important concept in disease causation is bias and confounding. Confounders can be due to a noncausal association between a given exposure and an outcome observed as a result of the influence of third variable


```{r}
grid.newpage()
exposure <-
  "Exposure
  (e.g. Coffee)"
expbox <- boxGrob(exposure, x=.2, y=.8)
outcome <-
  "Outcome
  (e.g. Lung Ca)"
outbox <- boxGrob(outcome, x=.8, y=.8)
confounder <-
  "Confounder
  (e.g. Smoking)"
confbox <- boxGrob(confounder, x=.5, y=.2)
connectGrob(expbox, outbox, "horizontal")
connectGrob(expbox, confbox, "vertical")
connectGrob(confbox, expbox, "vertical")
connectGrob(confbox, outbox, "vertical")

expbox
outbox
confbox
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

